On Devon Allen's Disqualification at the 2022 World Track and Field Championships

### 2023-09-08 Manuscript/manuscript.tex
fixed broken table

\begin{table}
  \centering
  \caption{Estimated parameters for the two effect GLMM on various data sets. SE
  is short for standard error. \eds{data in table needs to be revisited and table
	needs to be referenced within the text. Also, it needs to be clarified 
	somewhere that ``Old Pooled'' excludes 2022 and ``All Pooled'' includes 2022.}} 
  \begin{tabular}{c c c c c c}
      \toprule
      Dataset & AIC & $\sigma_h^2$ & $\sigma_v^2$ & $\alpha$ & $\delta_{i/j}$ \\
      \midrule
      Year Effect Only & $-2023.5$ & N/A & 0.048 & $-1.857$ & 0.152
      Heat Effect Only & $-2070.7$ & 0.073 & N/A & $-1.890$ & 0.135
      Full model & $-2075.7$ & 0.057 & 0.040 & $-1.880$ & 0.134 \\
      \bottomrule
  \end{tabular}
  \label{tab:Gamma_parameters}
\end{table}

>>>>

\begin{table}
  \centering
  \caption{Estimated parameters for the two effect GLMM on various data sets. SE
  is short for standard error. \eds{data in table needs to be revisited and table
	needs to be referenced within the text. Also, it needs to be clarified 
	somewhere that ``Old Pooled'' excludes 2022 and ``All Pooled'' includes 2022.}} 
  \begin{tabular}{c c c c c c}
      \toprule
      Dataset & AIC & $\sigma_h^2$ & $\sigma_v^2$ & $\alpha$ & $\delta_{i/j}$ \\
      \midrule
      Year Effect Only & $-2023.5$ &       & 0.048 & $-1.857$ & 0.152\\
      Heat Effect Only & $-2070.7$ & 0.073 &       & $-1.890$ & 0.135\\
      Full model       & $-2075.7$ & 0.057 & 0.040 & $-1.880$ & 0.134\\
      \bottomrule
  \end{tabular}
  \label{tab:Gamma_parameters}
\end{table}
